---
title: "Commercial Goals: Unique Member Receipts Logged Seasonal Trends"
subtitle: "Reviewing Seasonal Variation"
author: "Insights and Analytics | `r paste0('Last Updated: ', format(Sys.time(), '%d %B, %Y'))`"
output: 
  pagedreport::paged_windmill:
    front_img: "input/blowing rock (1).jpg"
    logo: "input/TangerOutlets_LOGO_horizontal.svg"
    img_to_dark: TRUE
    logo_to_white: TRUE
    toc: TRUE
knit: pagedown::chrome_print
toc-title: "Table of Contents"
main-color: "#bf0000"
secondary-color: "#acacad"
google-font: TRUE
main-font: "Roboto"
editor_options: 
  chunk_output_type: console
---

```{css, echo = FALSE}

p, ul, ol {
  margin-right: 0%;
}

h1.title {
    font-size: 30pt;
    margin-right: 10%;
    font-weight: 700;
}

h1.subtitle {
    font-size: 20pt;
    margin-right: 15%;
    font-weight: 300;
}

h2.author {
    font-size: 12pt;
    margin-right: 10%;
    font-weight: 700;
}

h2.date {
    font-size: 12pt;
    margin-right: 10%;
    font-weight: 300;
}

h1.toc-title {
    font-size: 30pt;
    font-weight: 200;
}

h1 { /* Header 1 */
  font-size: 26px;
}
h2 { /* Header 2 */
    font-size: 20px;
}
h3 { /* Header 3 */
  font-size: 16px;
}
body {
  font-size: 10pt;
}
```

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.align = 'center')
library(tidyverse)
library(prophet)
library(kableExtra)
library(gt)
library(geomtextpath)
options(scipen = 999)
theme_set(theme_bw())
cb_palette <- c("#003399", "#ff2b4f", "#3686d3", "#fcab27", "#88298a", "#000000", "#969696", "#008f05", "#FF5733", "#E5F828")

load(file = here::here("data", "CleanRecpts_Seas.rds"))

# ---- Different Combined -------

RecptMo <-
  CleanRecpts_Seas %>% 
  mutate(FirRecMo = lubridate::floor_date(FirRecPerYear, "month")) %>% 
  group_by(PurchYear, FirRecMo) %>% 
  summarise(CountCusFir = n()) %>% 
  ungroup() %>% 
  mutate(Month = lubridate::month(FirRecMo), #, label = T, abbr = T
         CountCusFir = as.numeric(CountCusFir))




RecptMo %>% 
    filter(PurchYear > 2016,
         PurchYear < 2022) %>% 
  mutate(Month = lubridate::month(FirRecMo, label=T, abbr = T)) %>% 
  select(-FirRecMo) %>% 
  pivot_wider(names_from = PurchYear, values_from = CountCusFir) %>% 
  gt(rowname_col = "Month") %>% 
  fmt_number(columns = 2:6,  decimals = 1,  suffix= T) %>% 
  tab_header(title = "Receipts: Count of Unique Customer ID's",
             subtitle = "With at least 1 logged receipt for that year | Counted in the month first Receipt is logged") %>% 
  summary_rows(
    # groups = TRUE,
    columns = c(2:6), fns = list(total = "sum"),  formatter = fmt_number,
    decimals = 1, suffix= T)#pattern = "{x}M" 



```

# Top Line {-}

We have provided historical trends for the past few years. The business owner for this metric will ultimately set where were they want the business goal to land.

For the members logging receipt seasonal trends, we have presented the count of unique customer id's for members who have logged a receipt within that calendar year. 


<style>
div.blue { background-color:#ff7a7a; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

__NOTE:__ This metric is only applicable to the yearly time horizon. It is possible that a member could log many receipts throughout a year or a member could log a single receipt. These types of member activity are counted equally by this metric.

</div>

<br>

```{r}

RecptMo %>% 
  filter(PurchYear >= 2016,
         PurchYear < 2022) %>% 
  group_by(PurchYear) %>% 
  summarise(TotalMem = sum(CountCusFir, na.rm = T)) %>% 
  ungroup() %>% 
  rename(`Unique Customers` = TotalMem) %>% 
  gt(rowname_col = "PurchYear") %>% 
  fmt_number(columns = 2,  decimals = 1,  suffix= T) %>% 
  tab_header(title = "Count of Unique Customer ID's By Year",
             subtitle = "With at least 1 logged receipt for that year")

```




# Reviewing Historical Data {-}

## Overview of Data {-}

For this analysis we have focused on analyzing the unique customers by day who have logged a receipt in the same month as their purchase date (note items purchased near the end of the month are less likely to be captured as there is a smaller time frame to log a receipt than those purchased at the start of the month).

We have focused on unique customers as they would be a foundational unit for this program (more unique customers would lead to more receipts and increase the likelihood of more total dollars captured). 


### Data Generation {-} 
Receipts as logged with TangStats. Note that we are only counting "approved" receipts and receipts that are logged in the same month as the purchase date.

### Data Pull from DB {-}
For forecasting purposes we have pulled data for all centers from 2016 until now (2022.01.28). The analysis excluded any data before 2015 as values were much lower.

__Source:__ TangStats (server: appsql-prod.database.windows.net)  

__Tables:__ [dbo].[tblReceiptTracking]

* Analyzing receipts that were logged in the same month as the purchase date. 
* Records with receipts that were larger than $100,000 were removed



\newpage

## Monthly Counts {-}

Each point represents the count of members where the first logged receipt was present in that month.

```{r}


(p1 <- RecptMo %>% 
  filter(PurchYear >= 2016) %>% 
  ggplot(aes(Month, CountCusFir, color=PurchYear))+
    geom_point()+
    # geom_line(size = 1.1)+
    geom_textpath(aes(label = PurchYear), size = 5, linewidth=1, alpha=0.7)+
    # geom_smooth(se=F)+
  scale_y_continuous(labels = scales::comma, breaks = seq(0,40000, 5000),expand = c(0,0), limits = c(0,40000))+
  scale_x_continuous(breaks = seq(1,12,1))+
  scale_color_manual(values = cb_palette)+
  labs(title ="Count of Unique Customer's First Reciept Logged Over Time",
       y = NULL, x="Month Number")+
  theme(legend.position = "none"))


```

\newpage

### Monthly Percentages {-}

Each point represents the percent of members where the first logged receipt was present in that month.

```{r, out.width="100%"}

(p2 <- RecptMo %>% 
  filter(PurchYear >= 2016,
         PurchYear < 2022) %>% 
  group_by(PurchYear) %>% 
  mutate(Perc = CountCusFir/ sum(CountCusFir)) %>% 
  ungroup() %>% 
  ggplot(aes(Month, Perc, fill=PurchYear))+
  # geom_point()+
  # geom_line(size = 1.1)+
  geom_bar(stat="identity", position = "dodge", alpha=0.7)+
  # geom_textpath(aes(label = PurchYear), size = 5, linewidth=1, alpha=0.7)+
  # geom_smooth(se=F)+
  scale_y_continuous(labels = scales::percent, breaks = seq(0,.21, .03), expand = c(0,0), limits = c(0, 0.21))+
  scale_x_continuous(breaks = seq(1,12,1))+
  scale_fill_manual(values = cb_palette)+
  labs(title ="Monthly Percent of Unique Customer's First Reciept Logged Over Time",
       y = NULL, x="Month Number", fill = "Receipt Year")+
   theme(legend.position = "bottom")
)

```


```{r, eval=F}
CleanRecpts_Seas %>% 
  filter(PurchYear >= 2016,
         PurchYear < 2022,
         CountRecPerYear <100) %>% 
  mutate(Month = lubridate::month(FirRecPerYear)) %>% 
  # group_by(PurchYear, Month) %>%
  # summarise()
  # ungroup() %>% 
  ggplot(aes(CountRecPerYear, fill=PurchYear))+
    geom_histogram(position = "dodge")
  
```



# Appendix {-}


## SQL: Receipts {-}

```{sql, eval=F, echo=T}
Select CustomerID, CenterID, TentID, CreatedOn, PurchaseDate, ReceiptAmount, MinsBtwnPurchAndSubmit 
	From (
		Select * 
			, datediff(minute, PurchaseDate, CreatedOn) as MinsBtwnPurchAndSubmit
		From tblReceiptTracking 
		Where Status = 'A'
			And DeletedOn is null 
			And TentID != 'TCPTS'
			And TentID is not null 
			And TentID != 'OTHER'
			And ReceiptAmount < 100000
	) a
```

## Forecast Model {-}

No forecast model was used to generate this data.